Racial and Ethnic Differences in ETI

### 2023-09-12 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti.qmd
table1 instead of gtsummary

```{r}
#| cache: true
by_year = encounter %>%
  group_by(eDWID, reviewyear) %>%
  summarise(across(c(race, Gender, WasGenotyped, F508_num, contains("insurance")), first),
    `Age at Last Visit` = last(na.omit(encounterage)),
    `Mean ppFEV` = mean(GLI_FEV1_pct_predicted, na.rm = T),
    `Weight at Last Visit` = last(na.omit(weight)),
    `Weight %ile at Last Visit` = last(na.omit(weightpercentile)),
    `BMI at Last Visit` = last(na.omit(bmivalue)),
    `BMI %ile at Last Visit` = last(na.omit(bmipercentile)),
    across(contains("Vx"), ~ max(.x)),
    .groups = "drop"
  ) %>%
  select(
    -eDWID, reviewyear, race, Gender, WasGenotyped, F508_num, contains("insurance"),
    `Age at Last Visit`, `Mean ppFEV`, `Weight at Last Visit`,
    `Weight %ile at Last Visit`, `BMI at Last Visit`,
    `BMI %ile at Last Visit`, contains("Vx")
  ) %>%
  rename(any_of(tidy_labels)) %>%
  tbl_summary(
    by = Year, missing_text = "Missing",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  bold_labels() %>%
  as_kable_extra()
```

>>>>

```{r}
#| cache: true
by_year = encounter %>%
  group_by(eDWID, reviewyear) %>%
  summarise(across(c(race, Gender, WasGenotyped, F508_num, contains("insurance")), first),
    `Age at Last Visit` = last(na.omit(encounterage)),
    `Mean ppFEV` = mean(GLI_FEV1_pct_predicted, na.rm = T),
    `Weight at Last Visit` = last(na.omit(weight)),
    `Weight %ile at Last Visit` = last(na.omit(weightpercentile)),
    `BMI at Last Visit` = last(na.omit(bmivalue)),
    `BMI %ile at Last Visit` = last(na.omit(bmipercentile)),
    across(contains("Vx"), ~ max(.x)),
    .groups = "drop"
  ) %>%
  select(
    -eDWID, reviewyear, race, Gender, WasGenotyped, F508_num, contains("insurance"),
    `Age at Last Visit`, `Mean ppFEV`, `Weight at Last Visit`,
    `Weight %ile at Last Visit`, `BMI at Last Visit`,
    `BMI %ile at Last Visit`, contains("Vx")
  ) %>%
  rename(any_of(tidy_labels))

```

```{r}
table1(~Gender+WasGenotyped+F508_num|race,data=by_year)
```
